Concurrent Programming in Harmony

### 2021-01-29 book/paper.tex
Forgot any/all

\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{len $e$} & cardinality \\
\hline
\texttt{$e$ - $e$} & set difference \\
\hline
\texttt{$e$ \& $e$ \& ...} & intersection \\
\hline
\texttt{$e$ | $e$ | ...} & union \\
\hline
\texttt{$e$ \string^ $e$ \string^ ...} & inclusion/exclusion (elements in odd number of sets) \\
\hline
\texttt{choose $e$} & select an element (Harmony will try all) \\
\hline
\texttt{min $e$} & minimum element \\
\hline
\texttt{max $e$} & maximum element \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{$d~k$} & indexing \\
\hline
\texttt{len $d$} & the number of keys in $d$ \\
\hline
\texttt{keys $d$} & the set of keys in $d$ \\
\hline
\texttt{$v$ [not] in keys $d$} & check if $v$ is a \emph{key} in $d$ \\
\hline
\texttt{$v$ [not] in $d$} & check if $v$ is a \emph{value} in $d$ \\
\hline
\texttt{$d$ \& $d$ \& ...} & dictionary intersection \\
\hline
\texttt{$d$ | $d$ | ...} & dictionary union \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{$t~k$} & indexing \\
\hline
\texttt{$t$ + $t$ + ...} & concatenation \\
\hline
\texttt{$t$ * $n$} & $n$ copies of $t$ concatenated \\
\hline
\texttt{$v$ [not] in $t$} & check if $v$ is a \emph{value} in $t$ \\
\hline
\texttt{len $t$} & the length of $t$ \\
\hline
\texttt{$t$ \& $t$ \& ...} & pairwise list minimum \\
\hline
\texttt{$t$ | $t$ | ...} & pairwise list maximum \\
\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{len $s$} & cardinality \\
\hline
\texttt{$s$ - $s$} & set difference \\
\hline
\texttt{$s$ \& $s$ \& ...} & intersection \\
\hline
\texttt{$s$ | $s$ | ...} & union \\
\hline
\texttt{$s$ \string^ $s$ \string^ ...} & inclusion/exclusion (elements in odd number of sets) \\
\hline
\texttt{choose $s$} & select an element (Harmony will try all) \\
\hline
\texttt{min $s$} & minimum element \\
\hline
\texttt{max $s$} & maximum element \\
\hline
\texttt{any $s$} & \texttt{True} if any value is \texttt{True} \\
\hline
\texttt{all $s$} & \texttt{True} if all values are \texttt{True} \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{$d~k$} & indexing \\
\hline
\texttt{len $d$} & the number of keys in $d$ \\
\hline
\texttt{keys $d$} & the set of keys in $d$ \\
\hline
\texttt{$v$ [not] in keys $d$} & check if $v$ is a \emph{key} in $d$ \\
\hline
\texttt{$v$ [not] in $d$} & check if $v$ is a \emph{value} in $d$ \\
\hline
\texttt{min $d$} & the minimum value in $d$ \\
\hline
\texttt{max $d$} & the maximum value in $d$ \\
\hline
\texttt{any $d$} & \texttt{True} if any value is \texttt{True} \\
\hline
\texttt{all $d$} & \texttt{True} if all values are \texttt{True} \\
\hline
\texttt{$d$ \& $d$ \& ...} & dictionary intersection \\
\hline
\texttt{$d$ | $d$ | ...} & dictionary union \\
\hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|l|l|}
\hline
\texttt{$t~k$} & indexing \\
\hline
\texttt{$t$ + $t$ + ...} & concatenation \\
\hline
\texttt{$t$ * $n$} & $n$ copies of $t$ concatenated \\
\hline
\texttt{$v$ [not] in $t$} & check if $v$ is a \emph{value} in $t$ \\
\hline
\texttt{len $t$} & the length of $t$ \\
\hline
\texttt{min $t$} & the minimum value in $t$ \\
\hline
\texttt{max $t$} & the maximum value in $t$ \\
\hline
\texttt{any $t$} & \texttt{True} if any value is \texttt{True} \\
\hline
\texttt{all $t$} & \texttt{True} if all values are \texttt{True} \\
\hline
\texttt{$t$ \& $t$ \& ...} & pairwise list minimum \\
\hline
\texttt{$t$ | $t$ | ...} & pairwise list maximum \\
\hline
\end{tabular}
\end{center}
